Case study validations of automatic bullet matching

### 2018-10-23 index.Rmd
color change?

```{r rocs, fig.cap="ROC curves for all studies based on land-to-land comparisons.", fig.width = 4.5, fig.height = 3, out.width = ".5\\textwidth"}
library(plotROC)
library(pROC)
all_lands %>% 
  ggplot(aes(colour = interaction(study, group1, sep = " "))) +
  geom_roc(aes(m = rfscore, d = as.numeric(sameland)), 
           labels =FALSE, pointsize = 0, alpha = 0.8) +
  theme_bw() +
  xlab("Fraction False Positives") +
  ylab("Fraction True Positives") +
  scale_colour_manual("Study", values = c("#fe9929", "#8856a7",
                                         "#74a9cf", "#2b8cbe", "#045a8d"))
```

>>>>

```{r rocs, fig.cap="ROC curves for all studies based on land-to-land comparisons.", fig.width = 4.5, fig.height = 3, out.width = ".5\\textwidth"}
library(plotROC)
library(pROC)
all_lands %>% 
  ggplot(aes(colour = interaction(study, group1, sep = " "))) +
  geom_roc(aes(m = rfscore, d = as.numeric(sameland)), 
           labels =FALSE, pointsize = 0, alpha = 0.8) +
  theme_bw() +
  xlab("Fraction False Positives") +
  ylab("Fraction True Positives") +
  scale_colour_manual("Study", values = c("#fe9929", "#aa0000",
                                         "#74a9cf", "#2b8cbe", "#045a8d"))
```
